\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
% pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
  \name{Chin Jia Hao}
  \program{BSc Hons in Computer Science - Cyber Security}
  \contact{\href{mailto:casualorient@gmail.com}{casualorient@gmail.com} \hspace{2cm} \href{tel:+60172412866}{+60 17-241 2866} \hspace{2cm}\href{https://www.linkedin.com/in/etcasual}{LinkedIn} \hspace{2cm}\href{https://github.com/etcasual}{GitHub} }
\end{resume_header}

\begin{resume_section}{About Me}
  \begin{nospacetabbing}
    \textbf{Aspiring Web Developer.}\\*
    Experienced in React framework. Well-versed in the world of TypeScript, NextJS and Firebase. \\*
    Worked on many personal projects for church, organizations and personal use. \\*
    \\*
    \textbf{Technical Skills}  \= TypeScript, React, HTML, CSS, SQL, NoSQL, Unix/Linux, Java, C/C++, Python\\*
    \textbf{Languages} \> Fluent in English, Chinese, Cantonese; Conversational Proficiency in Malay\\*
    \textbf{Interests} \> Programming, Gaming, Watching Movies\\*
  \end{nospacetabbing}

\end{resume_section}

\begin{resume_section}{Work Experience}
  \begin{resume_employer}{Appxplore Sdn. Bhd.}{Frontend Engineer}{Kuala Lumpur, MY}{September 2022 - Present}
    \item Built webpages with games and web3 integration, using wagmi, WalletConnect, viem.
    \item Managed a website revamp migrating most of the design to a new design and CSS animations.
    \item Handled a small portion of the backend written in Rust for API development.
    \item Built a web based admin panel for configuring web games using Framework7.
    \item Skills Used: React, PWA, MySQL, Web3, Rust, Framework7
  \end{resume_employer}

  \vspace{\baselineskip}

  \begin{resume_employer}{LS Smart Machinery}{Developer by Contact / Intern. Tech Team}{Kuala Lumpur, MY}{January 2021 - January 2022}
    \item One of the starting members of the team to build a Web Application to deliver a streamlined experience for sellers from stock taking to providing food delivery to customers.
    \item Handled payment integration.
    \item Led a newly joined intern in front-end operations.
    \item Skills Used: React, PWA, Supabase, Firebase.
  \end{resume_employer}
\end{resume_section}


\begin{resume_section}{Personal Projects}

  \begin{resume_subsection}[(June 2023 - Present)]{\href{https://github.com/etcasual/cyc-attendance}{Attendance Collection System for church [Ongoing Project]}}
    \begin{subitems}
      \item Building a website to ease attendance collection.
      \item Started a MySQL Database as the users data can be used and scalable in other church applications.
      \item used Argon to encrypt passwords before sending to db.
      \item Prisma, React Query, TRPC, Argon
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(March 2023)]{\href{https://github.com/etcasual/the-heirs}{The Heirs - Church Event Application}}
    \begin{subitems}
      \item Built a website as a chatroom for audience interaction.
      \item Autoscrolls to latest when a message is recieved.
      \item Devices will have a textbox to write messages and once sent, the messages will be presented on a huge screen.
      \item Animated Scroll, React, Firebase Realtime Database, form handling.
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(December 2022)]{\href{https://github.com/etcasual/wncd}{Warrior Nation Camp - In Time}}
    \begin{subitems}
      \item Built a website to collect registrations.
      \item the registrations are then read by the system as users database.
      \item Then transitioned into a game system where each group has a timer ticking down, and has to complete tasks to add time to their timer just like the movie: In Time.
      \item Has a voting system where groups vote for another group to recieve punishment.
      \item Has a master control page to control states for all participants to prompt votes on demand.
      \item Scores are transacted using encrypted QR Codes and specialised scanners.
      \item React, Firebase Realtime Database, Google Sheet API, AES Encrypt
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(April 2022)]{Freelancing - {\href{https://github.com/LFBFerreira/portfolio_website}{Luis Ferreira Portfolio} - {\href{https://luisferreira.tech}{Website Link}}}}
    \begin{subitems}
      \item Built a website according to design by the creator.
      \item Handled CI/CD and Deployment via Vercel.
      \item Vercel, React, p5js, Google Analytics, GSAP animations
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(April 2022)]{\href{https://github.com/marcustut/lightchaser}{LightChaser - Companion App for a Youth Camp}}
    \begin{subitems}
      \item Responsible for frontend aspects of the web application to support operations for the LightChaser camp.
      \item Handled a puzzle game within the application using Google Maps API and QR.
      \item Made a realtime interaction screen where users send emojis and the emojis will be shown on the screen.
      \item Vite, React, TailwindCSS, WebSocket
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(August 2021)]{\href{https://github.com/etcasual/fgacycyw}{YWKL PWA - Church application}}
    \begin{subitems}
      \item A Church Application by PWA to provide an environment for church operations.
      \item Database in Notion due to providing ease of access to data for administrative team.
      \item NextJS, React, TailwindCSS, Firebase Auth, PWA, Notion API
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(February 2022)]{\href{https://github.com/etcasual/ywreunion}{YW Reunion - A web-based realtime voting system}}
    \begin{subitems}
      \item Realtime voting system for an event and displaying the results in realtime.
      \item Firebase Realtime Database, React, Zustand State Management
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(July 2021)]{\href{https://github.com/etcasual/stumble-guys-cal}{Score Calculation System}}
    \begin{subitems}
      \item Score calculation system for game admins to easily calculate scores in an online competition.
      \item Firebase Firestore
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

  \begin{resume_subsection}[(April 2021)]{\href{https://github.com/etcasual/the-cure-discord}{The Cure Online Discord Bot}}
    \begin{subitems}
      \item Discord Bot to manage online operations for an online competition.
      \item Responsible for moderating announcements and webscraping.
      \item Axios, Node-TS, Heroku
    \end{subitems}
  \end{resume_subsection}

  \vspace{\baselineskip}

\begin{resume_subsection}[(October 2021)]{\href{https://github.com/etcasual/dtindahouse}{Wedding Website}}
  \begin{subitems}
    \item SPA for a wedding's landing page, RSVP.
    \item Embedded YouTube for livestream.
    \item React, YouTube API
  \end{subitems}
\end{resume_subsection}

\vspace{\baselineskip}

\begin{resume_subsection}[(July 2022)]{FYP Marketplace - {\href{https://github.com/etcasual/fypfrontend}{Frontend}} / {\href{https://github.com/etcasual/fypbackend}{Backend}}}
  \begin{subitems}
    \item FYP Project on Marketplace with native cryptocurrency.
    \item Backend uses solidity hardhat with Supabase.
    \item Frontend uses React, NextJS, Firebase Social Login.
    \item Solidity, Ethers, React, Next.Js, Firebase, Hardhat, Supabase, Node-TS, ImgBB API
  \end{subitems}
\end{resume_subsection}
\end{resume_section}

\begin{resume_section}{Education}
  \begin{resume_subsection}[Kuala Lumpur, MY (2019--2022)]{Asia Pacific University of Innovation and Technology}
    \begin{subitems}
      \item BSc in Computer Science - Cyber Security
      \item Diploma in Information Technology - Specialism in Software Engineering
    \end{subitems}
  \end{resume_subsection}

\end{resume_section}

\end{document}
